### 2013-05-22 doc/dissertation/document/chapters/mc_background/mc_background.tex
adding to rda section for sppn equations

\subsection{Reduced Domain Approximation}
\label{subsec:reduced_domain_approximation}
For scalable parallel implementations and efficient Monte Carlo
transport, the domain is required to be sparse. We may find through
general preconditioning operations as outlined by the Monte Carlo
problem in Eq~(\ref{eq:left_right_correction}) that this sparsity is
lost. To alleviate this, we propose modifying the domain sampled by
the Monte Carlo method to generate the correction within MCSA by
removing terms in the iteration matrix through some predetermined
criteria in order to recover sparsity. As the Neumann-Ulam scheme is a
stochastic realization of multiple matrix-vector multiplies, the
criteria we choose should be based on maintain those elements that
will make the largest contributions to the multiplication. For each
row in the preconditioned system, we can then apply the reduced domain
approximation to eliminate those elements that either fall below a
specified tolerance level, keep the $N$ largest elements in a row, or
both giving:
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = \ve{x}^k + \ve{r}^k\:,\\
    \ve{r}^{k+1/2} = \ve{b} - \ve{A}\ve{x}^{k+1/2}\:,\\
    \hat{\ve{A}}\delta\ve{x}^{k+1/2} = \ve{r}^{k+1/2}\:, 
    \label{eq:rda_correction}\\
    \ve{x}^{k+1} = \ve{x}^{k+1/2} + \delta \ve{x}^{k+1/2}\:,\\
    \ve{r}^{k+1} = \ve{b} - \ve{A}\ve{x}^{k+1}\:,
  \end{gather}
  \label{eq:rda_mcsa}
\end{subequations}
where $\hat{\ve{A}}$ in Eq~(\ref{eq:rda_correction}) means that the
reduced domain approximation has been applied to the iteration matrix
in the Monte Carlo method. If enough of the terms in the original
iteration matrix have been maintained, the character of the original
iteration matrix should be retained and continue to accelerate the
iterative scheme.

>>>>

\subsection{Reduced Domain Approximation}
\label{subsec:reduced_domain_approximation}
For scalable parallel implementations and efficient Monte Carlo
transport, the domain is required to be sparse. We may find through
general preconditioning operations as outlined by the Monte Carlo
problem in Eq~(\ref{eq:left_right_correction}) that this sparsity is
lost. To alleviate this, we propose modifying the domain sampled by
the Monte Carlo method to generate the correction within MCSA by
removing terms in the iteration matrix through some predetermined
criteria in order to recover sparsity. As the Neumann-Ulam scheme is a
stochastic realization of multiple matrix-vector multiplies, the
criteria we choose should be based on maintaining those elements that
will make the largest contributions to the multiplication and
therefore recover as much of the original product as possible. For
each row in the preconditioned system, we can then apply the reduced
domain approximation to eliminate those elements that either fall
below a specified tolerance level, keep the $N$ largest elements in
each row, or both giving:
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = \ve{x}^k + \ve{r}^k\:,\\
    \ve{r}^{k+1/2} = \ve{b} - \ve{A}\ve{x}^{k+1/2}\:,\\
    \hat{\ve{A}}\delta\ve{x}^{k+1/2} = \ve{r}^{k+1/2}\:, 
    \label{eq:rda_correction}\\
    \ve{x}^{k+1} = \ve{x}^{k+1/2} + \delta \ve{x}^{k+1/2}\:,\\
    \ve{r}^{k+1} = \ve{b} - \ve{A}\ve{x}^{k+1}\:,
  \end{gather}
  \label{eq:rda_mcsa}
\end{subequations}
where $\hat{\ve{A}}$ in Eq~(\ref{eq:rda_correction}) means that the
reduced domain approximation has been applied to the iteration matrix
in the Monte Carlo method. If enough of the terms in the original
iteration matrix have been maintained, the character of the original
iteration matrix should be retained and continue to accelerate the
iterative scheme. The effects of the reduced domain approximation on
systems where it is required due to the explicit preconditioning
strategy chosen will be presented in Chapter~\ref{ch:spn_equations}.

### 2013-05-22 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding to rda section for sppn equations

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/ilut_rda_iterations.pdf}
  \end{center}
  \caption{\textbf{Number of MCSA iterations required to converge the
      second eigenvalue iteration for the fuel assembly problem with
      ILUT preconditioning as a function of reduced domain
      approximation fill level.}  \textit{The largest fill level
      presented is that using the ILUT parameters that gave the best
      results with the approximation.}}
  \label{fig:ilut_rda_iterations}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/ilut_rda_quality.pdf}
  \end{center}
  \caption{\textbf{ILUT preconditioning quality metric for the fuel
      assembly problem given as a function of reduced domain
      approximation fill level.}  \textit{The largest fill level
      presented is that using the ILUT parameters that gave the best
      results with the approximation.}}
  \label{fig:ilut_rda_quality}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/spainv_rda_iterations.pdf}
  \end{center}
  \caption{\textbf{Number of MCSA iterations required to converge the
      second eigenvalue iteration for the fuel assembly problem with
      SPAINV preconditioning as a function of reduced domain
      approximation fill level.}  \textit{The largest fill level
      presented is that using the SPAINV parameters that gave the best
      results with the approximation.}}
  \label{fig:spainv_rda_iterations}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/spainv_rda_quality.pdf}
  \end{center}
  \caption{\textbf{SPAINV preconditioning quality metric for the fuel
      assembly problem given as a function of reduced domain
      approximation fill level.}  \textit{The largest fill level
      presented is that using the SPAINV parameters that gave the best
      results with the approximation.}}
  \label{fig:spainv_rda_quality}
\end{figure}

@@

>>>>

@@

@@

\subsection{Applying the Reduced Domain Approximation}
\label{subsec:spn_prec_rda}
For each preconditioning technique presented, although convergence was
achieved a primary concern is the number of non-zero states in each
row of the system generated by the explicit preconditioning
strategy. In many cases, orders of magnitude more matrix elements were
generated resulting in poor scalability for domain decomposed
algorithms. As outlined in
\S~\ref{subsec:reduced_domain_approximation}, the reduced domain
approximation may be used as a mechanism to potentially alleviate this
problem by filtering elements of the composite matrix in each row that
fall below a certain threshold value or by maintaining the largest $N$
elements in each row where $N$ is a designated fill level.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/rda_iterations.pdf}
  \end{center}
  \caption{\textbf{Number of MCSA iterations required to converge the
      second eigenvalue iteration for the fuel assembly problem with
      preconditioning as a function of reduced domain approximation
      fill level.}  \textit{The largest fill level for each
      preconditioning presented is that using the parameters that gave
      the best results without the approximation.}}
  \label{fig:rda_iterations}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/rda_quality.pdf}
  \end{center}
  \caption{\textbf{Preconditioning quality metric for the fuel
      assembly problem given as a function of reduced domain
      approximation fill level.}  \textit{The largest fill level for
      each preconditioning presented is that using the parameters that
      gave the best results without the approximation.}}
  \label{fig:rda_quality}
\end{figure}
